---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(heutools)
```
# Overview

This package is intended as a helper for common HEU functions.  In particular the aim is to help build consistency for plots and colours.

# Plots

The main function for plots is theme_heu() this is a base theme for use with plots, based on theme_minimal() with a few tweaks.

Additionally there is scale_fill_heu() and scale_colour_heu() which use the HEU colour palettes to provide fill and colours for ggplot.

# Colours

THe HEU uses NHS colours as it's baseline, with a few colours chosen out of the palette, but in principle any NHS colours can be used.

There are two functions directly linked to colours,

get_heu_colours() - this pulls the HEU colours from get_nhs_colours from the NHSRtheme package  


get_heu_palette() - this uses the HEU colours to build a palette for use within ggplot scale functions.


The last function is rgb2hex() which converts individual RGB colours on a 1 to 256 scale into hex values usable for ggplot - this is helpful when you don't have the palette but may be able to use colour picker in paint to approximate.
